Provisional Title

### 2021-05-08 draft/draft.tex
more intro, more refs

Microbial communities often invade one another.
This has been observed, for instance, 
in river courses where terrestrial microbial communities mix with aquatic microorganisms
\cite{Luo2020,Vass2021}
or in soil communities being invaded by aerially dispersed bacteria and funghi \cite{Evans2019}.
The human digestive system can even get invaded several times a day by the microbial consortia
that reside on the ingested food.
Ecologists have long contemplated the idea that interactions between multiple co-invading species
can produce correlated invasional outcomes
\cite{Gilpin1994,Grosholz2005,Green2011,Livingston2013,Rillig2015,OLoughlin2017}.
One example is the hypothesis known as \textit{invasional meltdown}, which proposes that
positive interactions between co-invading species can enhance their invasive success and
facilitate future invasions \cite{Simberloff1999,Simberloff2006,Gurevitch2006}.

The phenomenon by which entire microbiomes invade one another has been termed
\textit{community coalescence} \cite{Rillig2015}.
In spite of its clear potential importance, the role of coalescence in microbiome assembly is
only beginning to be addressed and little is known about the mechanisms that govern it and its
potential implications.
Early mathematical models of community-community invasions \cite{Gilpin1994,Toquenaga1997},
as well as more recent work including environmental construction (e.g., consumer-resource models)
\cite{Tikhonov2016,Tikhonov2017,Lechon2021}, suggest that high-order invasion effects are common
during community coalescence. Communities that have a previous history of coexistence may exhibit an
emergent ``cohesiveness'' which produces correlated invasional outcomes among species from the
same community \cite{Livingston2013,Sierocinski2017}.
The situation where ecological partners in the invading community recruit one another into the final
coalesced community has been called \textit{ecological co-selection} \cite{Rillig2017,Sierocinski2017}.

@@

>>>>

Microbial communities often invade one another.
This has been observed, for instance, 
in river courses where terrestrial microbial communities mix with aquatic microorganisms
\cite{Mansour2018,Luo2020,Vass2021}
or in soil communities being invaded as a result of
tillage and outplanting \cite{Rillig2016} or by
aerially dispersed bacteria and funghi \cite{Evans2019}.
The human digestive system can get invaded several times a day by the microbial consortia
that reside on the ingested food, and the skin microbiota is also subject to
invasions when making contact with environmental sources of microbes \cite{Vandegrift2019}.

The phenomenon by which entire microbiomes invade one another has been termed
\textit{community coalescence} \cite{Rillig2015}.
Ecologists have long contemplated the idea that interactions between multiple co-invading species
can produce correlated invasional outcomes
\cite{Gilpin1994,Grosholz2005,Green2011,Livingston2013,Rillig2015,OLoughlin2017,Castledine2020}.
One example is the hypothesis known as \textit{invasional meltdown}, which proposes that
positive interactions between co-invading species can enhance their invasive success and
facilitate future invasions \cite{Simberloff1999,Simberloff2006,Gurevitch2006}.
However, and
in spite of its clear potential importance, the role of coalescence in microbiome assembly is
only beginning to be addressed and little is known about the mechanisms that govern it and its
potential implications.
Early mathematical models of community-community invasions \cite{Gilpin1994,Toquenaga1997}
as well as more recent work
\cite{Tikhonov2016,Tikhonov2017,Vila2019,Lechon2021}
suggest that high-order invasion effects are common
during community coalescence. Communities that have a previous history of coexistence may exhibit an
emergent ``cohesiveness'' which produces correlated invasional outcomes among species from the
same community \cite{Livingston2013,Sierocinski2017}.
The situation where ecological partners in the invading community recruit each other into the final
coalesced community has been called \textit{ecological co-selection} \cite{Rillig2017,Sierocinski2017}.

The mechanisms of ecological co-selection during community coalescence are still poorly understood.
Do a few key species recruit everyone else, or are collective interactions among all species
(including the rarer members of the community) relevant for coalescence outcomes?
While it is reasonable to expect species with larger population sizes to have a proportionally oversized effect,
natural communities tend to be highly diverse \cite{Louca2016}
and
the role played by the less abundant species has long been subject to debate \cite{Winfree2015}.
Laboratory cultures have also been found to contain uneven distributions of multiple strains that feed
off the metabolic secretions of the dominant species \cite{Rosenzweig1994,Goldford2018}.
The fate of these sub-dominant taxa may be dependent on the invasional success of their dominant
species, or, alternatively, the dominant itself may owe its dominance (at least in part) to cross-feeding
or other forms of facilitation from the rarer members of the population.
These scenarios would give rise to ``top-down'' or ``bottom-up'' community cohesiveness, respectively.
Either of these forms of co-selection could, in principle, be positive (recruitment) or negative (antagonism),
as illustrated in \figref[e]{fig1}.
Which of these situations are typically found in nature?
Addressing this question has been experimentally challenging in the past \cite{Rillig2017,Sierocinski2017}.

\vspace{1.5cm}

Check this reference \cite{Castledine2020}

Uncovering the rules of microbial community invasions \cite{Vila2019}

@@

Resource availability modulates biodiversity–invasion relationships by altering competitive interactions \cite{Yang2017}

Resource pulses can alleviate the biodiversity–invasion relationship in soil microbial communities \cite{Mallon2015}
